Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2014-02-03 paper.tex
added scripts for generating RA codes.  Added metapost plot for turbo sync sims

Figure~\ref{fig:plotphaseQPSKmultL} shows the MSE of the phase estimator when $M=4$ and $L=32,256, 2048$ and the number of pilots is $\abs{P}=\tfrac{L}{8},L$.  The figure depicts an interesting phenomenon.  When $L=2048$ and $\abs{P} = \tfrac{L}{8} = 256$ the number of pilots symbols is the same as when $L=\abs{P} = 256$.  When the SNR is small (approximately less than \unit[0]{dB}) the least squares estimator using the $256$ pilots symbols and also the $2048-256=1792$ data symbols performs \emph{worse} than the estimator that uses only the $256$ pilots symbols.  A similar phenomenon occurs when $L=256$ and $\abs{P} = \tfrac{L}{8} = 32$.  This behaviour suggests that using the data symbols is counterproductive when the SNR is low.

@@

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM4-3.mps}
		\caption{Phase error versus SNR for QPSK.}
		\label{fig:plotphaseQPSKmultL}
\end{figure}

@@

Monte Carlo simulations were used to assess the performance of the least squares estimator and also to validate our asymptotic theory.  Interestingly, when the SNR is small, it is counterproductive to use the data symbols to estimate the phase (Figure~\ref{fig:plotphaseQPSKmultL}).  %This suggests the use of a weighted objective function, which would be an interesting topic for future research.
The simulations also indicate our estimator to be an effective initialiser for turbo synchronisation proceedures.

>>>>

%Figure~\ref{fig:plotphaseQPSKmultL} shows the MSE of the phase estimator when $M=4$ and $L=32,256, 2048$ and the number of pilots is $\abs{P}=\tfrac{L}{8},L$.  The figure depicts an interesting phenomenon.  When $L=2048$ and $\abs{P} = \tfrac{L}{8} = 256$ the number of pilots symbols is the same as when $L=\abs{P} = 256$.  When the SNR is small (approximately less than \unit[0]{dB}) the least squares estimator using the $256$ pilots symbols and also the $2048-256=1792$ data symbols performs \emph{worse} than the estimator that uses only the $256$ pilots symbols.  A similar phenomenon occurs when $L=256$ and $\abs{P} = \tfrac{L}{8} = 32$.  This behaviour suggests that using the data symbols is counterproductive when the SNR is low.

@@

% \begin{figure}[tp]
% 	\centering
% 		\includegraphics[width=\linewidth]{code/data/plotM4-3.mps}
% 		\caption{Phase error versus SNR for QPSK.}
% 		\label{fig:plotphaseQPSKmultL}
% \end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotturbo-1.mps}
		\caption{Probability of bit error $P_B$ with turbo synchronisation.}
		\label{fig:plotphaseQPSKmultL}
\end{figure}

@@

Monte Carlo simulations were used to assess the performance of the least squares estimator and also to validate our asymptotic theory.  %Interestingly, when the SNR is small, it is counterproductive to use the data symbols to estimate the phase (Figure~\ref{fig:plotphaseQPSKmultL}).  %This suggests the use of a weighted objective function, which would be an interesting topic for future research.
The simulations also indicate our estimator to be an effective initialiser for turbo synchronisation proceedures.
